\documentclass[a4paper,11pt]{article}
\pagestyle{empty} % No page numbers
\usepackage{geometry}
\geometry{margin=.7in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage[normalem]{ulem}

\def\jobh{\hspace{-1ex}}
\def\locationh{\hspace{7cm}}
\def\dateh{\hspace{3cm}}
\def\titlev{\vspace{.5cm}}
\def\sectionv{\vspace{.2cm}}
\def\subsectionv{\vspace{-5.3ex}}
\def\betweenpoints{.1cm}
\def\postpointsv{\vspace{0cm}}
\def\betweenjobsv{\vspace{0.4cm}}
\def\betweenskillsh{\hspace{1.4cm}}


\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Carlos Serrouya}} \\
    Calgary | www.linkedin.com/in/carlos-serrouya-27053b276 | \href{mailto:carlos.serrouya@ucalgary.ca}{carlos.serrouya@ucalgary.ca} | 250-837-1041 \\
\end{center}

\titlev

\noindent \makebox[\textwidth][c]{\textsc{Work Experience and Personal Projects}}
\vspace{-2.35em} % Adjust this value as needed
\par\noindent
\rule{\textwidth}{0.4pt}

\sectionv

\noindent \begin{tabbing}
    \locationh \= \kill
    \textbf{Data Science Intern} \> \textit{Alberta Biodiversity Monitoring Institute} \` 2023-2024 \\
\end{tabbing}


\begin{itemize}[leftmargin=.5cm, itemsep=.1cm, before=\subsectionv, after=\postpointsv]
    \item Developed machine learning models for animal detection, snow depth, and snow coverage in camera trap images.
    \item Implemented U-Net neural network, transfer learning, multiple regression, and random forests models using Keras/TensorFlow and Scikit-learn.
    \item Optimized image processing with NumPy/Pillow, reducing RAM and VRAM usage during training.
    \item Created object contouring, detection, and outlier detection algorithms.
    \item Managed large datasets with Pandas and SQL, integrated multiple regression models into SQL functions.
    \item Presented machine learning results to a non-technical panel, achieving 84\% snow depth accuracy and 96\% coverage classification.
    \item Reduced false positives in Microsoft's Megadetector by 72\%, false negatives by 9\%.
    \item Visualized model performance data with Matplotlib and Seaborn.
    \item Automated image/audio conversion on Linux servers, reducing file sizes for backup.
\end{itemize}

\betweenjobsv

\begin{tabbing}
    \locationh \= \kill
    \textbf{Personal Project} \> \textit{NFL Score Prediction Model} \` 2023 \\
\end{tabbing}

\begin{itemize}[leftmargin=.5cm, itemsep=.1cm, before=\subsectionv, after=\postpointsv]
    \item Used BeautifulSoup to scrape data from sports stats websites.
    \item Developed a predictive model for NFL game outcomes with 67\% accuracy on test data.
\end{itemize}

\betweenjobsv

\begin{tabbing}
    \locationh \= \kill
    \textbf{Server/Bartender/Host} \> \textit{Village Idiot Bar and Grill} \` 2016-2021 \\
\end{tabbing}

\begin{itemize}[leftmargin=.5cm, itemsep=.1cm, before=\subsectionv, after=\postpointsv]
    \item Worked in a high-paced environment, handled customer interactions, and managed cash transactions.
    \item Operated as part of a team, successfully mitigated conflicts and handled thousands of dollars each shift.
\end{itemize}

\betweenjobsv

\begin{tabbing}
    \locationh \= \kill
    \textbf{Basketball Coach} \> \textit{Revelstoke Secondary School} \` 2019-2021\\
\end{tabbing}

\begin{itemize}[leftmargin=.5cm, itemsep=.1cm, before=\subsectionv, after=\postpointsv]
    \item Volunteered to coach U13 basketball team while serving as the varsity team captain.
    \item Organized drills, coached games, and led practices.
    \item Awarded the Terry Beitel award for community athletic leadership and achievement.
\end{itemize}

\betweenjobsv

\noindent \makebox[\textwidth][c]{\textsc{Education and Certifications}}
\vspace{-2.35em} % Adjust this value as needed
\par\noindent
\rule{\textwidth}{0.4pt}

\sectionv

\noindent
\begin{minipage}[t]{0.45\textwidth} % Left column (45% of text width)
    \textbf{University of Calgary} \\
    \textit{BSc Computer Science} \hfill 2022-2026 \\
    \textit{BSc Mathematics} \hfill 2021-2026
\end{minipage}
\hfill % This creates space between the columns
\begin{minipage}[t]{0.45\textwidth} % Right column (45% of text width)
    \textbf{Coursera} \\
    \textit{Advanced Learning Algorithms} \hfill 2023 \\
    \textit{Regression \& Classification} \hfill 2023
\end{minipage}

\betweenjobsv
\sectionv

\noindent \makebox[\textwidth][c]{\textsc{Advanced Skills}}
\vspace{-2.35em} % Adjust this value as needed
\par\noindent
\rule{\textwidth}{0.4pt}

\sectionv

\noindent
\begin{minipage}[t]{0.32\textwidth} % Left column (32% of text width)
    \textbf{Microsoft Office} \\
    \textbf{Testing Automation} \\
\end{minipage}
\betweenskillsh
\begin{minipage}[t]{0.32\textwidth} % Middle column (32% of text width)
    \textbf{Data Validation} \\
    \textbf{Data Visualization} \\
\end{minipage}
\betweenskillsh
\begin{minipage}[t]{0.32\textwidth} % Right column (32% of text width)
    \textbf{SQL} \\
    \textbf{Power BI} \\
\end{minipage}

\end{document}

% \textbf{Basketball Coach} \hfill 2019-2021
% \begin{itemize}[leftmargin=0.5cm]
%     \item Volunteered to coach U13 basketball team while serving as the varsity team captain.
%     \item Organized drills, coached games, and led practices.
%     \item Awarded the Terry Bidel award for community athletic leadership and achievement.
% \end{itemize}